---
title: "Total Mixed Ration Characteristics In Dairy Cows"
output: 
  github_document:
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

# Statistical analysis preface 
Currently the following R packages were loaded

```{r }
library(readxl)

library("reshape2")

library("matrixStats")

library(rpart)

library(rattle)

library(rpart.plot)

library(RColorBrewer)

library("FactoMineR")

library("factoextra")

library("lme4") 

library("ggplot2")

library(devtools)

#install_github("vqv/ggbiplot", force=TRUE)

library(ggbiplot)

```


# Data extraction, transformation and loading

## TMR Data 

```{r}
TMR <- read.csv2("TMRAudits.csv")
TMR$Total <- NULL
TMR$Quantity <- NULL

TMR_wide <- dcast(TMR, Herd + Sieve ~ Sample) ## reshape table - wide format
TMR_wide[TMR_wide == "0"] <- NA

TMR_wide$mean <- rowMeans(TMR_wide[,3:12], na.rm = TRUE) ## Mean Sample 1 - 10

TMR_wide$diff <- (TMR_wide$refusals - TMR_wide$mean)/TMR_wide$mean ## relative difference between mean and orts

TMR_matrix <- as.matrix(TMR_wide[,3:12])
TMR_wide$sd <- rowSds(TMR_matrix, na.rm = TRUE) ## Standard deviation

CV <- function(mean, sd) { (sd/mean)*100 }
TMR_wide$cv <- CV(mean = TMR_wide$mean, sd = TMR_wide$sd) ## Coefficient of variation in TMR_wide$cv
```

### Making a new matrix with the means, cv, orts

```{r}
Herd <- matrix(TMR_wide$Herd, ncol = 3, byrow=TRUE)
colnames(Herd) <- c("Herd1","Herd2", "Herd")

mean <- matrix(TMR_wide$mean, ncol = 3, byrow = TRUE)
colnames(mean) <- c("FRESH.mid.mean","FRESH.pan.mean", "FRESH.top.mean")

cv <- matrix(TMR_wide$cv, ncol = 3, byrow = TRUE)
colnames(cv) <- c("FRESH.mid.cv","FRESH.pan.cv", "FRESH.top.cv")

diff <- matrix(TMR_wide$diff, ncol = 3, byrow = TRUE)
colnames(diff) <- c("REFUSALS.mid","REFUSALS.pan", "REFUSALS.top")

TMR_table <- data.frame(Herd, mean, cv, diff)
TMR_table <- na.omit(TMR_table[,3:12])
```

```{r}
summary(TMR_table)
```

```{r}
sd(TMR_table$FRESH.pan.mean)
sd(TMR_table$FRESH.mid.mean)
sd(TMR_table$FRESH.top.mean)
sd(TMR_table$FRESH.pan.cv)
sd(TMR_table$FRESH.mid.cv)
sd(TMR_table$FRESH.top.cv)
sd(TMR_table$REFUSALS.pan)
sd(TMR_table$REFUSALS.mid)
sd(TMR_table$REFUSALS.top)
```

### Check normality
```{r}
TMR_table$FRESH.top.cv <- log(TMR_table$FRESH.top.cv)
TMR_table$FRESH.mid.cv <- log(TMR_table$FRESH.mid.cv)
TMR_table$FRESH.pan.cv <- log(TMR_table$FRESH.pan.cv)
TMR_table$REFUSALS.top <- log(TMR_table$REFUSALS.top +1)

par(mfrow = c(3,3))
hist(TMR_table$FRESH.top.mean)
hist(TMR_table$FRESH.mid.mean)
hist(TMR_table$FRESH.pan.mean)
hist(TMR_table$FRESH.top.cv)
hist(TMR_table$FRESH.mid.cv)
hist(TMR_table$FRESH.pan.cv)
hist(TMR_table$REFUSALS.top)
hist(TMR_table$REFUSALS.mid)
hist(TMR_table$REFUSALS.pan)
```

```{r}
par(mfrow = c(3,3))
shapiro.test(TMR_table$FRESH.top.mean)
qqnorm(TMR_table$FRESH.top.mean); qqline(TMR_table$FRESH.top.mean)
shapiro.test(TMR_table$FRESH.mid.mean)
qqnorm(TMR_table$FRESH.mid.mean); qqline(TMR_table$FRESH.mid.mean)
shapiro.test(TMR_table$FRESH.pan.mean)
qqnorm(TMR_table$FRESH.pan.mean); qqline(TMR_table$FRESH.pan.mean)
shapiro.test(TMR_table$FRESH.top.cv)
qqnorm(TMR_table$FRESH.top.cv); qqline(TMR_table$FRESH.top.cv)
shapiro.test(TMR_table$FRESH.mid.cv)
qqnorm(TMR_table$FRESH.mid.cv); qqline(TMR_table$FRESH.mid.cv)
shapiro.test(TMR_table$FRESH.pan.cv)
qqnorm(TMR_table$FRESH.pan.cv); qqline(TMR_table$FRESH.pan.cv)
shapiro.test(TMR_table$REFUSALS.top)
qqnorm(TMR_table$REFUSALS.top); qqline(TMR_table$REFUSALS.top)
shapiro.test(TMR_table$REFUSALS.mid)
qqnorm(TMR_table$REFUSALS.mid); qqline(TMR_table$REFUSALS.mid)
shapiro.test(TMR_table$REFUSALS.pan)
qqnorm(TMR_table$REFUSALS.pan); qqline(TMR_table$REFUSALS.pan)
```

## SURVEY

```{r}
ENQ_data <- read.csv2("SURVEY.csv")
```

## Making a new matrix with TMR and SURVEY + data manipulation

```{r}
DATASET1 <- merge(TMR_table, ENQ_data, by.x = "Herd", by.y = "HERD", all = FALSE)

DATASET1$CONSERVATION_SCORE <- as.factor(DATASET1$CONSERVATION_SCORE)
DATASET1$CONSERVATION <- as.factor(DATASET1$CONSERVATION)
DATASET1$SPOILAGE <- as.factor(DATASET1$SPOILAGE)
DATASET1$SCRAPING_SCORE <- as.factor(DATASET1$SCRAPING_SCORE)
DATASET1$SCRAPING <- as.factor(DATASET1$SCRAPING)
DATASET1$HOR_VERT_DRUM <- as.factor(DATASET1$HOR_VERT_DRUM)
DATASET1$AUGER_SCORE <- as.factor(DATASET1$AUGER_SCORE)
DATASET1$AUGER <- as.factor(DATASET1$AUGER)
DATASET1$KNIVES_SCORE <- as.factor(DATASET1$KNIVES_SCORE)
DATASET1$KNIVES <- as.factor(DATASET1$KNIVES)
DATASET1$HAY_PROCESSING <- as.factor(DATASET1$HAY_PROCESSING)
DATASET1$POSITION <- as.factor(DATASET1$POSITION)
DATASET1$MIXING_START <- as.factor(DATASET1$MIXING_START)
DATASET1$MIXING_AFTER_LAST_MIN <- as.factor(DATASET1$MIXING_AFTER_LAST_MIN)
DATASET1$MIXING_AFTER_LAST <- as.factor(DATASET1$MIXING_AFTER_LAST)
DATASET1$LIQUID <- as.factor(DATASET1$LIQUID)
DATASET1$FILLING <- as.factor(DATASET1$FILLING)
DATASET1$RPM <- as.factor(DATASET1$RPM)
DATASET1$RPM_2 <- as.factor(DATASET1$RPM_2)
DATASET1$MOVEMENT_SCORE <- as.factor(DATASET1$MOVEMENT_SCORE)
DATASET1$MOVEMENT <- as.factor(DATASET1$MOVEMENT)
DATASET1$EMPTY <- as.factor(DATASET1$EMPTY)
```

```{r}
summary(DATASET1)
```

# Principal Component Analysis TMR

```{r}
TMR.pca <- prcomp(na.omit(DATASET1[,2:10]),
                 center = TRUE,
                 scale. = TRUE) 
print(TMR.pca)
```

```{r}
PC1PC2 <- read.csv2("PC1 and PC2 bar chart data.csv",dec = ".")
  
PC1PC2$PC1 <- as.numeric(PC1PC2$PC1)
PC1PC2$PC2 <- as.numeric(PC1PC2$PC2)
PC1PC2$screen <- factor(PC1PC2$Groups, levels= c("FRESHTOP,MEAN", "FRESHMID,MEAN", "FRESHPAN,MEAN", "FRESHTOP,CV", "FRESHMID,CV", "FRESHPAN,CV", "REFUSALSTOP", "REFUSALSMID", "REFUSALSPAN")) 

screenlabs <- c(expression("FRESH"[TOP.MEAN]), expression("FRESH"[MID.MEAN]), expression("FRESH"[PAN.MEAN]), 
                expression("FRESH"[TOP.CV]), expression("FRESH"[MID.CV]), expression("FRESH"[PAN.CV]), 
                expression("REFUSALS"[TOP]), expression("REFUSALS"[MID]), expression("REFUSALS"[PAN]))

```

```{r}
library(ggplot2)
library(forcats)

ggplot(data=PC1PC2, aes(x=fct_rev(screen), y=PC1)) +
  scale_x_discrete(labels= rev(screenlabs)) +
  xlab("") + ylab("") +
  geom_bar(position="dodge", stat="identity", fill="steelblue") +
  ylim(-0.6, 0.6) +
  coord_flip() +
  ggtitle("PC1") +
  theme_minimal()
```

```{r}
ggplot(data=PC1PC2, aes(x=fct_rev(screen), y=PC2)) +
  scale_x_discrete(labels= rev(screenlabs)) +
  xlab("") + ylab("") +
  geom_bar(position="dodge", stat="identity", fill="#009900") +
  ylim(-0.6, 0.6) +
  coord_flip() +
  ggtitle("PC2") +
  theme_minimal()
```

```{r}
PREDICT_PCA <- as.data.frame(predict(TMR.pca))
```

```{r}
plot(TMR.pca, type = "l")
```

```{r}
summary(TMR.pca)
```


```{r}
biplot(TMR.pca)

fviz_pca_var(TMR.pca, col.var = "black")
```

# Regression Tree TMR + SURVEY

## PC1

```{r}
fit <- rpart(PREDICT_PCA$PC1 ~ SPOILAGE + SCRAPING + HOR_VERT_DRUM + AUGER + KNIVES + HAY_PROCESSING + POSITION + MIXING_START + MIXING_AFTER_LAST + LIQUID + FILLING + RPM_2 + MOVEMENT + EMPTY, data = DATASET1, method="anova")

printcp(fit) # display the results 
plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# plot tree 
fancyRpartPlot(fit)
```

## PC2

```{r}
fit <- rpart(PREDICT_PCA$PC2 ~ SPOILAGE + SCRAPING + HOR_VERT_DRUM + AUGER + KNIVES + HAY_PROCESSING + POSITION + MIXING_START + MIXING_AFTER_LAST + LIQUID + FILLING + RPM_2 + MOVEMENT + EMPTY, data = DATASET1, method="anova")

printcp(fit) # display the results 
plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# plot tree 
fancyRpartPlot(fit)
```

# Factor Analysis of Mixed Data TMR + SURVEY

```{r}
datafamd <- na.omit(DATASET1[,c(2:10,        ## TMRaudit active
                                   13,16,22,23,26,  ## active categorical variables
                                   15,19,21,24,27,28,30,32,33         ## supplementary categorical variables 
                                   )])

datafamd$FRESH.top.mean <- scale((datafamd$FRESH.top.mean), center = TRUE, scale = TRUE)
datafamd$FRESH.mid.mean <- scale((datafamd$FRESH.mid.mean), center = TRUE, scale = TRUE)
datafamd$FRESH.pan.mean <- scale((datafamd$FRESH.pan.mean), center = TRUE, scale = TRUE)
datafamd$FRESH.top.cv <- scale((datafamd$FRESH.top.cv), center = TRUE, scale = TRUE)
datafamd$FRESH.mid.cv <- scale((datafamd$FRESH.mid.cv), center = TRUE, scale = TRUE)
datafamd$FRESH.pan.cv <- scale((datafamd$FRESH.pan.cv), center = TRUE, scale = TRUE)
datafamd$REFUSALS.top <- scale((datafamd$REFUSALS.top), center = TRUE, scale = TRUE)
datafamd$REFUSALS.mid <- scale((datafamd$REFUSALS.mid), center = TRUE, scale = TRUE)
datafamd$REFUSALS.pan <- scale((datafamd$REFUSALS.pan), center = TRUE, scale = TRUE)

summary(datafamd)

res.mfa <- FAMD(datafamd, graph=TRUE, sup.var=c(15:23))
print(res.mfa)
```

```{r}
eig.val <- get_eigenvalue(res.mfa)
head(eig.val)
```

## visualisations

```{r}
fviz_screeplot(res.mfa)
```

```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa, "var", 
             axes = 1)
```

```{r}
# Contribution to the second dimension
fviz_contrib(res.mfa, "var", 
             axes = 2)
```

```{r}
quanti.var <- get_famd_var(res.mfa, "quanti.var")
quanti.var 
```

```{r}
fviz_famd_var(res.mfa, "quanti.var", col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
```

```{r}
p <- fviz_famd_var(res.mfa, "quanti.var", label="none", col.var = "black")
p

p + annotate("text", x=.7, y=1.1, label=expression("FRESH"[TOP.MEAN]), size=3, angle=60) +
  annotate("text", x=1, y=.5, label=expression("FRESH"[PAN.CV]), size=3, angle=30) +
  annotate("text", x=1.1, y=.45, label=expression("FRESH"[MID.CV]), size=3, angle=25) +
  annotate("text", x=.65, y=-.45, label=expression("FRESH"[TOP.CV]), size=3, angle=330) +
  annotate("text", x=.75, y=-1, label=expression("REFUSALS"[TOP]), size=3, angle=310) +
  annotate("text", x=-.3, y=-1, label=expression("FRESH"[PAN.MEAN]), size=3, angle=76) +
  annotate("text", x=-0.8, y=-.65, label=expression("FRESH"[MID.MEAN]), size=3, angle=40) +
  annotate("text", x=-.9, y=0.40, label=expression("REFUSALS"[PAN]), size=3, angle=340) +
  annotate("text", x=-.95, y=0.7, label=expression("REFUSALS"[MID]), size=3, angle=330) +
  expand_limits(x=c(-1.5,1.5), y=c(-1.5,1.5))

```


```{r}
quali.var <- get_famd_var(res.mfa, "quali.var")
quali.var 
```

```{r}
plot(res.mfa, choix = "quali")
```


```{r}
fviz_famd_var(res.mfa, "quali.var", repel = TRUE, col.var = "black")
```

```{r}
fviz_famd_ind(res.mfa, col.ind = "cos2", geom=c("point", "text"),
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE, invisible = "quali.var")
```

```{r}
fviz_ellipses(res.mfa, c("POSITION", "SPOILAGE", "HOR_VERT_DRUM", "HAY_PROCESSING", "MIXING_AFTER_LAST"), repel = TRUE)
```

# MPR + ENQ

## Making a new matrix with MPR and SELECTED SURVEY VARIABLES

```{r}
MPR <- read.csv2("MPR_data.csv")
summary(MPR)

sd(MPR$COWS)
sd(MPR$DIM)
sd(MPR$KGMILK)
sd(MPR$FPCM)
sd(MPR$FAT)
sd(MPR$PROTEIN)
sd(MPR$KGFP)
sd(na.omit(MPR$AGE_YEAR))

par(mfrow = c(3,3))
hist(MPR$DIM)
hist(MPR$KGMILK)
hist(MPR$FPCM)
hist(MPR$FAT)
hist(MPR$PROTEIN)
hist(MPR$KGFP)
hist(MPR$AGE_YEAR)
```

```{r}
par(mfrow = c(3,3))
shapiro.test(MPR$DIM)
qqnorm(MPR$DIM); qqline(MPR$DIM)
shapiro.test(MPR$KGMILK)
qqnorm(MPR$KGMILK); qqline(MPR$KGMILK)
shapiro.test(MPR$FPCM)
qqnorm(MPR$FPCM); qqline(MPR$FPCM)
shapiro.test(MPR$FAT)
qqnorm(MPR$FAT); qqline(MPR$FAT)
shapiro.test(MPR$PROTEIN)
qqnorm(MPR$PROTEIN); qqline(MPR$PROTEIN)
shapiro.test(MPR$KGFP)
qqnorm(MPR$KGFP); qqline(MPR$KGFP)
shapiro.test(MPR$AGE_YEAR)
qqnorm(MPR$AGE_YEAR); qqline(MPR$AGE_YEAR)
```

```{r}
DATASET2 <- merge(MPR, DATASET1, by.x= 'HERD', by.y= "Herd", all = FALSE)
summary(DATASET2)

sd(DATASET2$COWS)
sd(DATASET2$DIM)
sd(DATASET2$KGMILK)
sd(DATASET2$FPCM)
sd(DATASET2$FAT)
sd(DATASET2$PROTEIN)
sd(DATASET2$KGFP)
sd(na.omit(DATASET2$AGE_YEAR))
```


```{r}
DATASET2.pca <- prcomp(na.omit(DATASET2[,c(2:8,10,11:19)]),
                 center = TRUE,
                 scale. = TRUE) 
print(DATASET2.pca)
```

```{r}
summary(DATASET2.pca)

PREDICT_PCAmilk <- as.data.frame(predict(DATASET2.pca))
```

## visualisations

```{r}
# Contribution to PC1
fviz_contrib(DATASET2.pca, "var", 
             axes = 1)
```

```{r}
# Contribution to PC2
fviz_contrib(DATASET2.pca, "var", 
             axes = 2)
```


```{r}
biplot(DATASET2.pca)

fviz_pca_var(DATASET2.pca, col.var = "black")
```

```{r}
p <- fviz_pca_biplot(DATASET2.pca, label="none", invisible ="ind", col.var = "black", xlim=c(-8, 8), ylim=c(-8, 8))
p
```

```{r}
p <- p + annotate("text", x=-0.15, y=6.2, label=expression("FRESH"[TOP.CV]), size=3, angle=274) +
  annotate("text", x=-0.5, y=5.3, label=expression("FRESH"[PAN.MEAN]), size=3, angle=280) +
  annotate("text", x=0.8, y=3.5, label=expression("COWS"), size=3, angle=70) +
  annotate("text", x=1.5, y=3.5, label=expression("FRESH"[PAN.CV]), size=3, angle=55) +
  annotate("text", x=2.75, y=2.1, label=expression("FRESH"[MID.CV]), size=3, angle=20) +
  annotate("text", x=2.2, y=1.2, label=expression("DIM"), size=3, angle=18) +
  annotate("text", x=3, y=.7, label=expression("PROTEIN"), size=3, angle=10) +
  annotate("text", x=1.8, y=-2.5, label=expression("FAT"), size=3, angle=320) +
  annotate("text", x=2.7, y=-5, label=expression("FRESH"[TOP.MEAN]), size=3, angle=315) +
  annotate("text", x=1, y=-3.5, label=expression("REFUSALS"[MID]), size=3, angle=300) +
  annotate("text", x=-1.8, y=-2.8, label=expression("AGE"), size=3, angle=50) +
  annotate("text", x=-6, y=-.8, label=expression("FPCM; KGFP"), size=3, angle=5) +
  annotate("text", x=-5.7, y=0, label=expression("KGMILK"), size=3, angle=0) +
  annotate("text", x=-1.7, y=0.5, label=expression("REFUSALS"[PAN]), size=3, angle=0) +
  annotate("text", x=-3.2, y=2.3, label=expression("FRESH"[MID.MEAN]), size=3, angle=345) +
  annotate("text", x=-2.2, y=3.5, label=expression("REFUSALS"[TOP]), size=3, angle=320)

p <- p + labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)")
p
  
```

```{r}
g <- fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), invisible = "var" , col.ind = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), xlim=c(-8, 8), ylim=c(-8, 8))
g <- g + labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)")
print (g)

```

```{r}
DATASETLAST <- DATASET2[-c(4,34), ]

fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$SPOILAGE, palette = c("#00AFBB", "#FC4E07"), addEllipses = TRUE, invisible = "var", col.var = "black")

```

```{r}
g <- ggbiplot(DATASET2.pca, choices = c(1,2), obs.scale = 1, var.scale = 1)
g <- g + geom_point(aes(size = DATASETLAST$FPCM, color = DATASETLAST$SPOILAGE))
g <- g + theme(legend.direction = 'horizontal', 
               legend.position = 'top')
g <- g + theme_minimal()
print(g)

g <- ggbiplot(DATASET2.pca, choices = c(1,2), obs.scale = 1, var.scale = 1, var.axes=FALSE) +
  geom_point(aes(size = DATASETLAST$FPCM, color = DATASETLAST$SPOILAGE)) +
  theme(legend.direction = 'horizontal', legend.position = 'top') +
  scale_size_continuous(name = "FPCM (kg)") +
  scale_color_manual(values = c("#00AFBB", "#FC4E07"), name = "Spoilage") +
  labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)") + 
  theme_minimal()
print(g)
```


```{r}
fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$POSITION, palette = c("#FC4E07", "#00AFBB"), addEllipses = TRUE, invisible = "var", col.var = "black")
```

```{r}
g <- ggbiplot(DATASET2.pca, choices = c(1,2), obs.scale = 1, var.scale = 1, var.axes=FALSE) +
  geom_point(aes(size = DATASETLAST$FPCM, color = DATASETLAST$POSITION)) +
  theme(legend.direction = 'horizontal', legend.position = 'top') +
  scale_size_continuous(name = "FPCM (kg)") +
  scale_color_manual (values = c("#FC4E07", "#00AFBB"), name = "Position", 
                      breaks=c("Good position", "Bad position")) +
  labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)") + 
  theme_minimal()
print(g)
```


```{r}
fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$MIXING_AFTER_LAST , addEllipses = TRUE, ellipse.type = "confidence", invisible = "var", label = "ind" , col.var = "black")
```

```{r}
fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$MOVEMENT, addEllipses = TRUE, ellipse.type = "confidence", label = "ind" , invisible = "var", col.var = "black")
```
