---
title: "Total Mixed Ration Characteristics In Dairy Cows"
output: 
  github_document:
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

This is an R Markdown Notebook for the TMR data of Leen Lietaer. When you execute code within the notebook, the results appear beneath the code.

First we need to load libraries. These are small packages of software we will use during our analysis.

```{r}
if (!require("readxl")) {
  install.packages("readxl", dependencies = TRUE)
  library(readxl)
}

if (!require("reshape2")) {
  install.packages("reshape2", dependencies = TRUE)
  library(reshape2)
}

if (!require("matrixStats")) {
  install.packages("matrixStats", dependencies = TRUE)
  library(matrixStats)
}

if (!require("rpart")) {
  install.packages("rpart", dependencies = TRUE)
  library(rpart)
}

if (!require("rattle")) {
  install.packages("rattle", dependencies = TRUE)
  library(rattle)
}

if (!require("rpart.plot")) {
  install.packages("rpart.plot", dependencies = TRUE)
  library(rpart.plot)
}

if (!require("RColorBrewer")) {
  install.packages("RColorBrewer", dependencies = TRUE)
  library(RColorBrewer)
}

if (!require("FactoMineR")) {
  install.packages("FactoMineR", dependencies = TRUE)
  library(FactoMineR)
}

if (!require("factoextra")) {
  install.packages("factoextra", dependencies = TRUE)
  library(factoextra)
}

if (!require("lme4")) {
  install.packages("lme4", dependencies = TRUE)
  library(lme4)
}

if (!require("ggplot2")) {
  install.packages("ggplot2", dependencies = TRUE)
  library(ggplot2)
}

if (!require("devtools")) {
  install.packages("devtools", dependencies = TRUE)
  library(devtools)
} 

if (!require("ggbiplot")) {
  install_github("vqv/ggbiplot", force=TRUE)
  library(ggbiplot)
}

if (!require("forcats")) {
  install.packages("forcats", force=TRUE)
  library(forcats)
}
```

TMR Consistency Data
====================

## Importing the TMR Consistency Data

```{r}
TMR <- read.csv2("TMRAudits.csv")
TMR$Total <- NULL
TMR$Quantity <- NULL

TMR_wide <- dcast(TMR, Herd + Sieve ~ Sample) ## reshape table - wide format
TMR_wide[TMR_wide == "0"] <- NA

TMR_wide$mean <- rowMeans(TMR_wide[,3:12], na.rm = TRUE) ## Herd mean of fresh sample 1 to 10

TMR_wide$diff <- (TMR_wide$refusals - TMR_wide$mean)/TMR_wide$mean ## relative difference between mean and refusals

TMR_matrix <- as.matrix(TMR_wide[,3:12])
TMR_wide$sd <- rowSds(TMR_matrix, na.rm = TRUE) ## Standard deviation of fresh sample 1 to 10

CV <- function(mean, sd) { (sd/mean)*100 }
TMR_wide$cv <- CV(mean = TMR_wide$mean, sd = TMR_wide$sd) ## Coefficient of variation
```

Making a new matrix with the mean, cv and relative difference between mean and refusals

```{r}
Herd <- matrix(TMR_wide$Herd, ncol = 3, byrow=TRUE)
colnames(Herd) <- c("Herd1","Herd2", "Herd")

mean <- matrix(TMR_wide$mean, ncol = 3, byrow = TRUE)
colnames(mean) <- c("FRESH.mid.mean","FRESH.pan.mean", "FRESH.top.mean")

cv <- matrix(TMR_wide$cv, ncol = 3, byrow = TRUE)
colnames(cv) <- c("FRESH.mid.cv","FRESH.pan.cv", "FRESH.top.cv")

diff <- matrix(TMR_wide$diff, ncol = 3, byrow = TRUE)
colnames(diff) <- c("REFUSALS.mid","REFUSALS.pan", "REFUSALS.top")

TMR_table <- data.frame(Herd, mean, cv, diff)
TMR_table <- na.omit(TMR_table[,3:12])
```

## Exploring the TMR Consistency Data

```{r}
summary(TMR_table)
```

```{r}
sd(TMR_table$FRESH.pan.mean)
sd(TMR_table$FRESH.mid.mean)
sd(TMR_table$FRESH.top.mean)
sd(TMR_table$FRESH.pan.cv)
sd(TMR_table$FRESH.mid.cv)
sd(TMR_table$FRESH.top.cv)
sd(TMR_table$REFUSALS.pan)
sd(TMR_table$REFUSALS.mid)
sd(TMR_table$REFUSALS.top)
```

Checking normality of the TMR Consistency Data

```{r}
TMR_table$FRESH.top.cv <- log(TMR_table$FRESH.top.cv)
TMR_table$FRESH.mid.cv <- log(TMR_table$FRESH.mid.cv)
TMR_table$FRESH.pan.cv <- log(TMR_table$FRESH.pan.cv)
TMR_table$REFUSALS.top <- log(TMR_table$REFUSALS.top +1)

par(mfrow = c(3,3))
hist(TMR_table$FRESH.top.mean)
hist(TMR_table$FRESH.mid.mean)
hist(TMR_table$FRESH.pan.mean)
hist(TMR_table$FRESH.top.cv)
hist(TMR_table$FRESH.mid.cv)
hist(TMR_table$FRESH.pan.cv)
hist(TMR_table$REFUSALS.top)
hist(TMR_table$REFUSALS.mid)
hist(TMR_table$REFUSALS.pan)
```

```{r}
par(mfrow = c(3,3))
shapiro.test(TMR_table$FRESH.top.mean)
qqnorm(TMR_table$FRESH.top.mean); qqline(TMR_table$FRESH.top.mean)
shapiro.test(TMR_table$FRESH.mid.mean)
qqnorm(TMR_table$FRESH.mid.mean); qqline(TMR_table$FRESH.mid.mean)
shapiro.test(TMR_table$FRESH.pan.mean)
qqnorm(TMR_table$FRESH.pan.mean); qqline(TMR_table$FRESH.pan.mean)
shapiro.test(TMR_table$FRESH.top.cv)
qqnorm(TMR_table$FRESH.top.cv); qqline(TMR_table$FRESH.top.cv)
shapiro.test(TMR_table$FRESH.mid.cv)
qqnorm(TMR_table$FRESH.mid.cv); qqline(TMR_table$FRESH.mid.cv)
shapiro.test(TMR_table$FRESH.pan.cv)
qqnorm(TMR_table$FRESH.pan.cv); qqline(TMR_table$FRESH.pan.cv)
shapiro.test(TMR_table$REFUSALS.top)
qqnorm(TMR_table$REFUSALS.top); qqline(TMR_table$REFUSALS.top)
shapiro.test(TMR_table$REFUSALS.mid)
qqnorm(TMR_table$REFUSALS.mid); qqline(TMR_table$REFUSALS.mid)
shapiro.test(TMR_table$REFUSALS.pan)
qqnorm(TMR_table$REFUSALS.pan); qqline(TMR_table$REFUSALS.pan)
```

Questionnaire data
==================

## Importing the Questionnaire Data

```{r}
ENQ_data <- read.csv2("SURVEY.csv")
```

Dataset Questionnaire
=====================

Making a new matrix with TMR Consistency and Questionnaire Data
Subsequently some columns are categories

```{r}
DATASET1 <- merge(TMR_table, ENQ_data, by.x = "Herd", by.y = "HERD", all = FALSE)

DATASET1$CONSERVATION_SCORE <- as.factor(DATASET1$CONSERVATION_SCORE)
DATASET1$CONSERVATION <- as.factor(DATASET1$CONSERVATION)
DATASET1$SPOILAGE <- as.factor(DATASET1$SPOILAGE)
DATASET1$SCRAPING_SCORE <- as.factor(DATASET1$SCRAPING_SCORE)
DATASET1$SCRAPING <- as.factor(DATASET1$SCRAPING)
DATASET1$HOR_VERT_DRUM <- as.factor(DATASET1$HOR_VERT_DRUM)
DATASET1$AUGER_SCORE <- as.factor(DATASET1$AUGER_SCORE)
DATASET1$AUGER <- as.factor(DATASET1$AUGER)
DATASET1$KNIVES_SCORE <- as.factor(DATASET1$KNIVES_SCORE)
DATASET1$KNIVES <- as.factor(DATASET1$KNIVES)
DATASET1$HAY_PROCESSING <- as.factor(DATASET1$HAY_PROCESSING)
DATASET1$POSITION <- as.factor(DATASET1$POSITION)
DATASET1$MIXING_START <- as.factor(DATASET1$MIXING_START)
DATASET1$MIXING_AFTER_LAST_MIN <- as.factor(DATASET1$MIXING_AFTER_LAST_MIN)
DATASET1$MIXING_AFTER_LAST <- as.factor(DATASET1$MIXING_AFTER_LAST)
DATASET1$LIQUID <- as.factor(DATASET1$LIQUID)
DATASET1$FILLING <- as.factor(DATASET1$FILLING)
DATASET1$RPM <- as.factor(DATASET1$RPM)
DATASET1$RPM_2 <- as.factor(DATASET1$RPM_2)
DATASET1$MOVEMENT_SCORE <- as.factor(DATASET1$MOVEMENT_SCORE)
DATASET1$MOVEMENT <- as.factor(DATASET1$MOVEMENT)
DATASET1$EMPTY <- as.factor(DATASET1$EMPTY)
```

## Exploring Dataset Questionnaire

```{r}
summary(DATASET1)
```

## Principal Component Analysis TMR Consistency Data

```{r}
TMR.pca <- prcomp(na.omit(DATASET1[,2:10]),
                 center = TRUE,
                 scale. = TRUE) 
print(TMR.pca)
```

Visualising contribution of variables to PC1 and PC2 by bar charts

```{r}
PC1PC2 <- read.csv2("PC1 and PC2 bar chart data.csv",dec = ".")
  
PC1PC2$PC1 <- as.numeric(PC1PC2$PC1)
PC1PC2$PC2 <- as.numeric(PC1PC2$PC2)
PC1PC2$screen <- factor(PC1PC2$Groups, levels= c("FRESHTOP,MEAN", "FRESHMID,MEAN", "FRESHPAN,MEAN", "FRESHTOP,CV", "FRESHMID,CV", "FRESHPAN,CV", "REFUSALSTOP", "REFUSALSMID", "REFUSALSPAN")) 

screenlabs <- c(expression("FRESH"[TOP.MEAN]), expression("FRESH"[MID.MEAN]), expression("FRESH"[PAN.MEAN]), 
                expression("FRESH"[TOP.CV]), expression("FRESH"[MID.CV]), expression("FRESH"[PAN.CV]), 
                expression("REFUSALS"[TOP]), expression("REFUSALS"[MID]), expression("REFUSALS"[PAN]))

```

```{r}
ggplot(data=PC1PC2, aes(x=fct_rev(screen), y=PC1)) +
  scale_x_discrete(labels= rev(screenlabs)) +
  xlab("") + ylab("") +
  geom_bar(position="dodge", stat="identity", fill="steelblue") +
  ylim(-0.6, 0.6) +
  coord_flip() +
  ggtitle("PC1") +
  theme_minimal()
```

```{r}
ggplot(data=PC1PC2, aes(x=fct_rev(screen), y=PC2)) +
  scale_x_discrete(labels= rev(screenlabs)) +
  xlab("") + ylab("") +
  geom_bar(position="dodge", stat="identity", fill="#009900") +
  ylim(-0.6, 0.6) +
  coord_flip() +
  ggtitle("PC2") +
  theme_minimal()
```

```{r}
PREDICT_PCA <- as.data.frame(predict(TMR.pca))
```

```{r}
plot(TMR.pca, type = "l")
```

```{r}
summary(TMR.pca)
```

Plotting variables and herds in relation to PC1 and PC2

```{r}
biplot(TMR.pca)

fviz_pca_var(TMR.pca, col.var = "black")
```

## Regression Trees for Dataset Questionnaire

Building regression trees to order the qualitative questionnaire variables hierarchically according to their contribution in variability of the Dataset Questionnaire

### PC1

```{r}
fit <- rpart(PREDICT_PCA$PC1 ~ SPOILAGE + SCRAPING + HOR_VERT_DRUM + AUGER + KNIVES + HAY_PROCESSING + POSITION + MIXING_START + MIXING_AFTER_LAST + LIQUID + FILLING + RPM_2 + MOVEMENT + EMPTY, data = DATASET1, method="anova")

printcp(fit) # display the results 
plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# plot tree 
fancyRpartPlot(fit)
```

### PC2

```{r}
fit <- rpart(PREDICT_PCA$PC2 ~ SPOILAGE + SCRAPING + HOR_VERT_DRUM + AUGER + KNIVES + HAY_PROCESSING + POSITION + MIXING_START + MIXING_AFTER_LAST + LIQUID + FILLING + RPM_2 + MOVEMENT + EMPTY, data = DATASET1, method="anova")

printcp(fit) # display the results 
plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# plot tree 
fancyRpartPlot(fit)
```

## Factor Analysis of Mixed Data - Dataset Questionnaire

The most important questionnaire variables from the regression tree analysis were set as active variables in the following factor analysis of mixed data (FAMD), the others were set as supplementary variables

```{r}
datafamd <- na.omit(DATASET1[,c(2:10,        ## TMRaudit active
                                   13,16,22,23,26,  ## active categorical variables
                                   15,19,21,24,27,28,30,32,33         ## supplementary categorical variables 
                                   )])

datafamd$FRESH.top.mean <- scale((datafamd$FRESH.top.mean), center = TRUE, scale = TRUE)
datafamd$FRESH.mid.mean <- scale((datafamd$FRESH.mid.mean), center = TRUE, scale = TRUE)
datafamd$FRESH.pan.mean <- scale((datafamd$FRESH.pan.mean), center = TRUE, scale = TRUE)
datafamd$FRESH.top.cv <- scale((datafamd$FRESH.top.cv), center = TRUE, scale = TRUE)
datafamd$FRESH.mid.cv <- scale((datafamd$FRESH.mid.cv), center = TRUE, scale = TRUE)
datafamd$FRESH.pan.cv <- scale((datafamd$FRESH.pan.cv), center = TRUE, scale = TRUE)
datafamd$REFUSALS.top <- scale((datafamd$REFUSALS.top), center = TRUE, scale = TRUE)
datafamd$REFUSALS.mid <- scale((datafamd$REFUSALS.mid), center = TRUE, scale = TRUE)
datafamd$REFUSALS.pan <- scale((datafamd$REFUSALS.pan), center = TRUE, scale = TRUE)

summary(datafamd)

res.mfa <- FAMD(datafamd, graph=TRUE, sup.var=c(15:23))
print(res.mfa)
```

Eigenvalues of the model

```{r}
eig.val <- get_eigenvalue(res.mfa)
head(eig.val)
```

```{r}
fviz_screeplot(res.mfa)
```

Visualising contribution of variables to DIM1 and DIM2 by bar charts

```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa, "var", 
             axes = 1)
```

```{r}
# Contribution to the second dimension
fviz_contrib(res.mfa, "var", 
             axes = 2)
```

Quantitative variables

```{r}
quanti.var <- get_famd_var(res.mfa, "quanti.var")
quanti.var 
```

```{r}
fviz_famd_var(res.mfa, "quanti.var", col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
```

Making plot more readable

```{r}
p <- fviz_famd_var(res.mfa, "quanti.var", label="none", col.var = "black")
p

p + annotate("text", x=.7, y=1.1, label=expression("FRESH"[TOP.MEAN]), size=3, angle=60) +
  annotate("text", x=1, y=.5, label=expression("FRESH"[PAN.CV]), size=3, angle=30) +
  annotate("text", x=1.1, y=.45, label=expression("FRESH"[MID.CV]), size=3, angle=25) +
  annotate("text", x=.65, y=-.45, label=expression("FRESH"[TOP.CV]), size=3, angle=330) +
  annotate("text", x=.75, y=-1, label=expression("REFUSALS"[TOP]), size=3, angle=310) +
  annotate("text", x=-.3, y=-1, label=expression("FRESH"[PAN.MEAN]), size=3, angle=76) +
  annotate("text", x=-0.8, y=-.65, label=expression("FRESH"[MID.MEAN]), size=3, angle=40) +
  annotate("text", x=-.9, y=0.40, label=expression("REFUSALS"[PAN]), size=3, angle=340) +
  annotate("text", x=-.95, y=0.7, label=expression("REFUSALS"[MID]), size=3, angle=330) +
  expand_limits(x=c(-1.5,1.5), y=c(-1.5,1.5))

```

Qualitative variables

```{r}
quali.var <- get_famd_var(res.mfa, "quali.var")
quali.var 
```

```{r}
plot(res.mfa, choix = "quali")
```

```{r}
fviz_famd_var(res.mfa, "quali.var", repel = TRUE, col.var = "black")
```

Plotting herds in relation to DIM1 and DIM2 

```{r}
fviz_famd_ind(res.mfa, col.ind = "cos2", geom=c("point", "text"),
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE, invisible = "quali.var")
```

Coloring herds in function of their answer to questionnaire questions: position, spoilage, mixer wagon type (horizontal / vertical), hay pre-processing, mixing time after last added ingredient

```{r}
fviz_ellipses(res.mfa, c("POSITION", "SPOILAGE", "HOR_VERT_DRUM", "HAY_PROCESSING", "MIXING_AFTER_LAST"), repel = TRUE)
```

Milk Records Data
=================

## Importing the Milk Records data
## Exploring the Milk Records data

```{r}
MPR <- read.csv2("MPR_data.csv")
summary(MPR)

sd(MPR$COWS)
sd(MPR$DIM)
sd(MPR$KGMILK)
sd(MPR$FPCM)
sd(MPR$FAT)
sd(MPR$PROTEIN)
sd(MPR$KGFP)
sd(na.omit(MPR$AGE_YEAR))
```

Checking normality of the Milk Records data (Quantitative variables)

```{r}
par(mfrow = c(3,3))
hist(MPR$DIM)
hist(MPR$KGMILK)
hist(MPR$FPCM)
hist(MPR$FAT)
hist(MPR$PROTEIN)
hist(MPR$KGFP)
hist(MPR$AGE_YEAR)
```

```{r}
par(mfrow = c(3,3))
shapiro.test(MPR$DIM)
qqnorm(MPR$DIM); qqline(MPR$DIM)
shapiro.test(MPR$KGMILK)
qqnorm(MPR$KGMILK); qqline(MPR$KGMILK)
shapiro.test(MPR$FPCM)
qqnorm(MPR$FPCM); qqline(MPR$FPCM)
shapiro.test(MPR$FAT)
qqnorm(MPR$FAT); qqline(MPR$FAT)
shapiro.test(MPR$PROTEIN)
qqnorm(MPR$PROTEIN); qqline(MPR$PROTEIN)
shapiro.test(MPR$KGFP)
qqnorm(MPR$KGFP); qqline(MPR$KGFP)
shapiro.test(MPR$AGE_YEAR)
qqnorm(MPR$AGE_YEAR); qqline(MPR$AGE_YEAR)
```

Dataset Milk
============

Making a new matrix: Milk Records Data and some variables selected from the Questionnaire Dataset

## Exploring Dataset Milk

```{r}
DATASET2 <- merge(MPR, DATASET1, by.x= 'HERD', by.y= "Herd", all = FALSE)
summary(DATASET2)

sd(DATASET2$COWS)
sd(DATASET2$DIM)
sd(DATASET2$KGMILK)
sd(DATASET2$FPCM)
sd(DATASET2$FAT)
sd(DATASET2$PROTEIN)
sd(DATASET2$KGFP)
sd(na.omit(DATASET2$AGE_YEAR))
```

## Principal Component Analysis Dataset Milk (Quantitative Variables)

```{r}
DATASET2.pca <- prcomp(na.omit(DATASET2[,c(2:8,10,11:19)]),
                 center = TRUE,
                 scale. = TRUE) 
print(DATASET2.pca)
```

```{r}
summary(DATASET2.pca)

PREDICT_PCAmilk <- as.data.frame(predict(DATASET2.pca))
```

Visualising contribution of variables to PC1 and PC2 by bar charts

```{r}
# Contribution to PC1
fviz_contrib(DATASET2.pca, "var", 
             axes = 1)
```

```{r}
# Contribution to PC2
fviz_contrib(DATASET2.pca, "var", 
             axes = 2)
```

Plotting variables and herds in relation to PC1 and PC2

```{r}
biplot(DATASET2.pca)

fviz_pca_var(DATASET2.pca, col.var = "black")
```

Making plot more readable

```{r}
p <- fviz_pca_biplot(DATASET2.pca, label="none", invisible ="ind", col.var = "black", xlim=c(-8, 8), ylim=c(-8, 8))
p
```

```{r}
p <- p + annotate("text", x=-0.15, y=6.2, label=expression("FRESH"[TOP.CV]), size=3, angle=274) +
  annotate("text", x=-0.5, y=5.3, label=expression("FRESH"[PAN.MEAN]), size=3, angle=280) +
  annotate("text", x=0.8, y=3.5, label=expression("COWS"), size=3, angle=70) +
  annotate("text", x=1.5, y=3.5, label=expression("FRESH"[PAN.CV]), size=3, angle=55) +
  annotate("text", x=2.75, y=2.1, label=expression("FRESH"[MID.CV]), size=3, angle=20) +
  annotate("text", x=2.2, y=1.2, label=expression("DIM"), size=3, angle=18) +
  annotate("text", x=3, y=.7, label=expression("PROTEIN"), size=3, angle=10) +
  annotate("text", x=1.8, y=-2.5, label=expression("FAT"), size=3, angle=320) +
  annotate("text", x=2.7, y=-5, label=expression("FRESH"[TOP.MEAN]), size=3, angle=315) +
  annotate("text", x=1, y=-3.5, label=expression("REFUSALS"[MID]), size=3, angle=300) +
  annotate("text", x=-1.8, y=-2.8, label=expression("AGE"), size=3, angle=50) +
  annotate("text", x=-6, y=-.8, label=expression("FPCM; KGFP"), size=3, angle=5) +
  annotate("text", x=-5.7, y=0, label=expression("KGMILK"), size=3, angle=0) +
  annotate("text", x=-1.7, y=0.5, label=expression("REFUSALS"[PAN]), size=3, angle=0) +
  annotate("text", x=-3.2, y=2.3, label=expression("FRESH"[MID.MEAN]), size=3, angle=345) +
  annotate("text", x=-2.2, y=3.5, label=expression("REFUSALS"[TOP]), size=3, angle=320)

p <- p + labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)")
p
```

Plotting herds in relation to PC1 and PC2

```{r}
g <- fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), invisible = "var" , col.ind = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), xlim=c(-8, 8), ylim=c(-8, 8))
g <- g + labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)")
print (g)

```

Coloring herds in function of their answer to questionnaire questions: spoilage, position, mixing time after the last added ingredient, movement (different visualisations, with or without taking herd mean milk yield in account)

```{r}
DATASETLAST <- DATASET2[-c(4,34), ]

fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$SPOILAGE, palette = c("#00AFBB", "#FC4E07"), addEllipses = TRUE, invisible = "var", col.var = "black")

```

```{r}
g <- ggbiplot(DATASET2.pca, choices = c(1,2), obs.scale = 1, var.scale = 1)
g <- g + geom_point(aes(size = DATASETLAST$FPCM, color = DATASETLAST$SPOILAGE))
g <- g + theme(legend.direction = 'horizontal', 
               legend.position = 'top')
g <- g + theme_minimal()
print(g)

g <- ggbiplot(DATASET2.pca, choices = c(1,2), obs.scale = 1, var.scale = 1, var.axes=FALSE) +
  geom_point(aes(size = DATASETLAST$FPCM, color = DATASETLAST$SPOILAGE)) +
  theme(legend.direction = 'horizontal', legend.position = 'top') +
  scale_size_continuous(name = "FPCM (kg)") +
  scale_color_manual(values = c("#00AFBB", "#FC4E07"), name = "Spoilage") +
  labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)") + 
  theme_minimal()
print(g)
```

```{r}
fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$POSITION, palette = c("#FC4E07", "#00AFBB"), addEllipses = TRUE, invisible = "var", col.var = "black")
```

```{r}
g <- ggbiplot(DATASET2.pca, choices = c(1,2), obs.scale = 1, var.scale = 1, var.axes=FALSE) +
  geom_point(aes(size = DATASETLAST$FPCM, color = DATASETLAST$POSITION)) +
  theme(legend.direction = 'horizontal', legend.position = 'top') +
  scale_size_continuous(name = "FPCM (kg)") +
  scale_color_manual (values = c("#FC4E07", "#00AFBB"), name = "Position", 
                      breaks=c("Good position", "Bad position")) +
  labs(x = "PC1 (21.4%)", y = "PC2 (16.3%)") + 
  theme_minimal()
print(g)
```

```{r}
fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$MIXING_AFTER_LAST , addEllipses = TRUE, ellipse.type = "confidence", invisible = "var", label = "ind" , col.var = "black")
```

```{r}
fviz_pca_biplot(DATASET2.pca, geom=c("point", "text"), habillage = DATASETLAST$MOVEMENT, addEllipses = TRUE, ellipse.type = "confidence", label = "ind" , invisible = "var", col.var = "black")
```
